Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-05-15 manuscript-figures.Rmd
add figures

```{r fig-5_Topt, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.

@@

```{r fig-6_CT_Width, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal tolerance range, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low.'}
# Shows how the parasite thermal niche (temperatures between CT_min and CT_max) 
# depends on vertebrate host availability (density and biting tolerance) in each
# of the focal systems.

>>>>

```{r fig-5_Topt, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.

@@

```{r fig-6_CT_Width, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal tolerance range, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low.'}
# Shows how the parasite thermal niche (temperatures between CT_min and CT_max) 
# depends on vertebrate host availability (density and biting tolerance) in each
# of the focal systems.
